TBD

### 2021-03-15 outputs/paper/paper.Rmd
updated OLS
still need to sort out fixed effects to get appropriate results. seems a prop test is probably necessary according to the stata files of the authors.

library(tidyverse)
library(ggplot2)
library(ggalt)
library(ggthemes)
library(kableExtra)
library(janitor)
library(dplyr)
# install.packages("olsrr")
library(olsrr)

@@

### OLS formula : y = mx + c, where 
### y = response (dependent variable) - so report/no report,
### m = slope
### x = independent variable, predictor - condition (no money, money, big money)
### c = the intercept
s8_money <-
  dfBehavModel %>%
  filter(cond == 1 | cond == 2 | cond == 3)
ols_regress(response ~ cond + male + above40 + computer + coworkers + other_bystanders, data = s8_money)

s8_no_money <-
  dfBehavModel %>%
  filter(cond == 0)
ols_regress(response ~ cond + male + above40 + computer + coworkers + other_bystanders, data = s8_no_money)

# need to control for treatment + institution + city 
```

>>>>

library(tidyverse)
library(ggplot2)
library(ggalt)
library(ggthemes)
library(kableExtra)
library(janitor)
library(dplyr)

library(olsrr)
library(plm)

@@

### OLS formula : y = mx + c, where 
### y = response (dependent variable) - so report/no report,
### m = slope
### x = independent variable, predictor - condition (no money, money, big money)
### c = the intercept

# conditions
# 0 - no money, 1 - money, 2 - big money, 3 - money no key.

# controls:
  # fixed effects for institution and city
  # treatment condition
# binary controls:
  # male, above 40, coworkers, computer, bystanders

s8 <- dfBehavModel %>%
  filter(cond == 0 | cond == 1)

### money vs no money

# proportional test

# regression (for whatever reason, can't do fixed effects for city + institution using plm without issues)

s8_main_result <- lm(response ~ cond, data = s8)
summary(s8_main_result)

# regression by country

s8_by_country <- lm(response ~ cond + male + above40 + coworkers + computer + other_bystanders, data = s8)
summary(s8_by_country)

# final table (S8)
